Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft

### 2016-04-11 presentation/presentation.tex
added an outline to the presentation
Added current capabilities

% presentation info
\title[Short Title]{GAS Quad}
\author{Smart Person}
\institute[MAGICC Lab]{\includegraphics[height=0.5in]{logo_gray}}
\date{\today}

@@

>>>>

% presentation info
\title{Multi-dimensional Optimization of Gasoline-fueled Variable Pitch Multirotor Aircraft}
%\title[Short Title]{GAS Quad}
\author{Dallin Briggs, Gary Ellingson}
\institute[MAGICC Lab]{\includegraphics[height=0.5in]{logo_gray}}
\date{\today}

@@

\begin{frame}{Outline}
\begin{itemize}
	\item{Motivation and Background}
	\item{---figure of multirotor trends in flight time}
	\item{---focus on OTS stuff bases our design on empirical models}

	\item{Theory - models}
	\item{---Engine model}
	\item{---Aero model}

	\item{Optimization}
	\item{---Objective only directly a function of 2 design variables}
	\item{---constraints}

	\item{Results}
	\item{lessons learned}
	\item{questions}
\end{itemize}
\end{frame}

\begin{frame}{Motivation and Background}
	\begin{center}
	Currently available multirotor capabilities
	\end{center}
	\begin{figure}
		\begin{center}
			\includegraphics[width=.70\textwidth]{current_capabilities.png}
			\label{current_capabilities}
		\end{center}
	\end{figure}
\end{frame}

\begin{frame}{Models}
	\begin{itemize}
		\item{To represent the aerodynamics of each rotor, we used Combined Differential Blade Element and Momentum Theory for nonuniform inflow.}
		\begin{center}
		$ dT = \frac{1}{2} \rho a \Omega^2 r^2 (\theta - \phi) c \  dr $

		$ dQ = \frac{1}{2} \rho \Omega^2 r^3 c (\delta + \phi C_L) \ dr $
		\end{center}
	\end{itemize}

\begin{frame}{Optimization Method}
